
\def\blanktext{The rest of this page is intentionally left blank.}

\begin{titlepage}
\pagestyle{empty}
% First Title Page
\text{ }\\[1in]\begin{center} \Huge \textbf{\sc \firstTitle} \end{center} 
% Blank Page
\newpage\text{\blanktext} 
% Second Title Page
\clearpage \text{ }\\[30pt]
\noindent\Large \authname \\[50pt]
\noindent\Huge \textbf{\firstTitle} \\[20pt]
\noindent\Large\textbf{\secondTitle} 
\\[25pt] \noindent\large\edition \ Edition
\vfill \normalsize
% Copyright Page
\newpage \text{ } \vfill  \footnotesize  \text{ } \\[7pt]
ISBN: \isbn \\[10pt]
\copyright \authname. 
All rights reserved. \\ \\ \\ 
This work is subject to copyright. \\ \\ 
This work may not be translated in whole or in part without the written permission of \publisher\ except for brief excerpts in 
connection with reviews or scholarly analysis.  Use in connection with any form of information storage retrieval, 
electronic adaption, computer software, or by similar or dissimilar methodology now known or hereafter developed is forbidden. \\ \\ 
The use in this publication of trade names, trademarks, service marks, and similar terms, even if they are not identified as 
such, is not to be taken as an expression of opinion as to whether or not they are subject to proprietary rights. \\ \\ 
Neither the Authors, nor the Publishers, nor the Editors give any warranty, express or implied, with respect to the material 
contained herein or for any any errors or omissions that may have been made.  \\ \\  
Typeset with \LaTeX \, and written in the United States of America.  
\\[2pt] \HRule \\[0.5cm]  \authname \\ \cred \\ \website
\end{titlepage}

